Four reasons your build is slow

### 2019-01-17 paper.tex
moved a citation to end of line

Makefiles are a collection of rules which describe how to build targets \cite{gnumakemanual},
and each rule consists
of a a series of prerequisites and a series of recipes which are run to build the target.  The
prerequisites can be built in parallel, but the recipes must be run in the order they are listed.  So,
the author of a makefile can directly impact the potential parallelism of the build by
how they organize their makefile.  It is possible to unnecessarily list things as recipes that
could have run in parallel.  Here we will look at an example of this and how our tool can
discover that these recipes don't actually need to run in parallel.

>>>>

Makefiles are a collection of rules which describe how to build targets,
and each rule consists
of a a series of prerequisites and a series of recipes which are run to build the target \cite{gnumakemanual}.  The
prerequisites can be built in parallel, but the recipes must be run in the order they are listed.  So,
the author of a makefile can directly impact the potential parallelism of the build by
how they organize their makefile.  It is possible to unnecessarily list things as recipes that
could have run in parallel.  Here we will look at an example of this and how our tool can
discover that these recipes don't actually need to run in parallel.
